### 2017-05-30 doc/experiments.tex
experiments section edited.

In the following sections, we report a series of experiments in which
we explore the kinds of linguistic regularities the
networks learn from
word-level input. Section~\ref{sec:macro} presents the macro-level
analyses where we propose methods to analyze the final hidden activation 
vectors of the recurrent pathways from linguistic point of view. 
Section~\ref{sec:micro} reports exploratory experiments on
the linguistic features encoded by individual hidden units. 
In both sections we report our findings based on the {\sc Imaginet}
model, discuss the generalizabilty of our methods to other architectures.
\label{edit:experimentsgeneral}, and whenever appropriate compare to
our two other models, {\sc LM} and {\sc Sum}.  For all the
experiments, we trained {\sc Imaginet} on the training portion of the
MSCOCO image-caption dataset \cite{lin2014microsoft}, and analyzed the
representations of the sentences in the validation set corresponding
to 5000 randomly chosen images. The target image representations were
extracted from the pre-softmax layer of the 16-layer CNN of
\namecite{simonyan2014very}.

>>>>

In the following section, we report a series of experiments in which
we explore the kinds of linguistic regularities the networks learn from
word-level input. Sections~\ref{sec:computeomission} to \ref{sec:beyondlexical} 
present the analyses of the final hidden activation 
vectors of the recurrent pathways from a linguistic point of view. 
Sections~\ref{sec:syntacticdim} and \ref{seq:describe} report exploratory experiments on
the linguistic features encoded by individual hidden dimensions. 
In all these experiments we report our findings based on the {\sc Imaginet}
model, whenever appropriate compare to our two other models {\sc LM} and {\sc Sum}, 
and discuss the generalizabilty of our methods to other architectures.
\label{edit:experimentsgeneral}
For all the experiments, we trained the models on the training portion of the
MSCOCO image-caption dataset \cite{lin2014microsoft}, and analyzed the
representations of the sentences in the validation set corresponding
to 5000 randomly chosen images. The target image representations were
extracted from the pre-softmax layer of the 16-layer CNN of
\namecite{simonyan2014very}.
